---
title: "R Notebook"
output: html_notebook
---

Create new master file with the following fields:
- playerid
- Player
- birth_year
- cbs_name



```{r}

library(tidyr)
library(dplyr)
library(stringr)
library("lubridate")
library(rvest)
#library(Lahman)

source('./daflFunctions.r')

year <- '2022'

getAge <- function(playerid) {
  print(playerid)
  Sys.sleep(60)
  byear <- NA
  tryCatch(
    {
      page <- read_html(str_c("https://www.fangraphs.com/players/nolan-jones/",playerid,"/stats"))
      byear <- page %>% html_node(".player-info__bio-birthdate td") %>% html_text() %>% 
      str_extract("[0-9/]{8,}") %>% mdy() %>% year()
    },
    error=function(error_message) {
      print("some error")
    }
  )
  print(byear)
  byear
}

read.cbs2 <- function(fn) {
  df <- read.csv(fn,skip=1,stringsAsFactors=FALSE, encoding="UTF-8")
  df <- mutate(df, Pos = pullPos(Player))
  df <- mutate(df, MLB = pullMLB(Player))
  df$Player <- unlist(lapply(df$Player,stripName))
  # Team abbreviations are not the same - find all discrepancies WAS->WSH
  df$MLB <- replace(df$MLB,df$MLB=='WAS','WSN')
  df$MLB <- replace(df$MLB,df$MLB=='CWS','CHW')
  df$MLB <- replace(df$MLB,df$MLB=='TB','TBR')
  df$MLB <- replace(df$MLB,df$MLB=='KC','KCR')
  df$MLB <- replace(df$MLB,df$MLB=='SD','SDP')
  df$MLB <- replace(df$MLB,df$MLB=='SF','SFG')

  # Create Team column
  #df <- mutate(df,Avail=str_replace(Avail,'\\.\\.\\.',''))
  #df <- left_join(df,nicks,by=c('Avail'))
  df$Team <- df$Avail
  #df$Team <- str_replace(df$Team,'W','Free Agent')
  df$Team <- ifelse(str_detect(df$Team,'W '),'Free Agent',df$Team)
  df <- select(df,-Avail)
  #addPlayerid(df)
}

```
Start with previous mymaster (playerid,Player,birth_year,cbs_name)
```{r}
mymaster <- read.csv("../mymaster.csv",stringsAsFactors=FALSE) %>% select(-X)

#cleanup any blank cbs_name
mymaster <- mutate(mymaster,cbs_name = ifelse(cbs_name=='',Player,cbs_name))
```



Start with a fangraphs ATC prediction file
Usually about 1400 players
Get Player, Team, playerid from here
Have to convert Team to MLB
```{r}

#fgh <- read.csv(str_c('../atcH',as.character(year),'.csv',sep=''),stringsAsFactors=FALSE, encoding="UTF-8")
fgh <- read.csv('../steamerHROS.csv',stringsAsFactors=FALSE, encoding="UTF-8")
#fgh <- read.csv('../batxHROS.csv',stringsAsFactors=FALSE, encoding="UTF-8")

colnames(fgh)[1] <- 'Player'
fgh <- select(fgh,playerid,Player,MLB=Team)

#fgp <- read.csv(str_c('../atcP',as.character(year),'.csv',sep=''),stringsAsFactors=FALSE, encoding="UTF-8")
fgp <- read.csv('../steamerPROS.csv',stringsAsFactors=FALSE, encoding="UTF-8")

colnames(fgp)[1] <- 'Player'
fgp <- select(fgp,playerid,Player,MLB=Team)

fgraphs <- bind_rows(fgh,fgp)

# This is for ATC files
#mlbmap <- read.csv("../data/MLBmap.csv",stringsAsFactors = FALSE)
#fgraphs <- left_join(fgraphs,mlbmap)

fgraphs <- filter(fgraphs,str_length(MLB)>0)

noidmatch <- anti_join(fgraphs,mymaster,by=c('playerid'))

```
For matches, update MLB for trades, signings
```{r}
small <- select(fgraphs,playerid,MLB)
mymaster <- left_join(mymaster,small,by=c('playerid'))
mymaster <- mutate(mymaster,MLB=ifelse(is.na(MLB.y),MLB.x,MLB.y)) %>% select(-MLB.x,-MLB.y)

```



If name and team are identical, replace the id
```{r}
sameName <- inner_join(noidmatch,mymaster,by=c('Player','MLB'))
repl <- select(sameName,playerid = playerid.y,newid = playerid.x)
mymaster <- left_join(mymaster,repl)
mymaster <- mutate(mymaster,playerid = ifelse(is.na(newid),playerid,newid)) %>% select(-newid)
```

If name is identical but team is different - update id AND MLB
```{r}
noidmatch2 <- anti_join(fgraphs,mymaster,by=c('playerid'))
sameName2 <- inner_join(noidmatch2,mymaster,by=c('Player'))

repl2 <- select(sameName2,playerid = playerid.y,newid = playerid.x,MLB = MLB.y, newMLB = MLB.x)
mymaster <- left_join(mymaster,repl2)
mymaster <- mutate(mymaster,playerid = ifelse(is.na(newid),playerid,newid)) %>% select(-newid)
mymaster <- mutate(mymaster,MLB = ifelse(is.na(newMLB),MLB,newMLB)) %>% select(-newMLB)
```
Add new rows

```{r}
noidmatch <- anti_join(fgraphs,mymaster,by=c('playerid')) %>% mutate(birth_year=NA,cbs_name=Player,Pos='')
addthem <- noidmatch %>% select(playerid,Player,birth_year,cbs_name,Pos,MLB)

mymaster <- bind_rows(mymaster,addthem)


```



What can I get from CBS?
There are a lot more rows in CBS than in fangraphs
```{r}
cbsH <- read.cbs2('../AllHitters.csv')
cbsH <- select(cbsH,Player,Pos,MLB)
cbsP <- read.cbs2('../AllPitchers01.csv')
cbsP <- select(cbsP,Player,Pos,MLB)
cbs <- bind_rows(cbsH,cbsP)

my <- mutate(mymaster,Player=cbs_name)

nonamecbs <- anti_join(cbs,my,by=c('Player'))

# Need to create new rows - need playerid, Player, birth_date, cbs_name, Pos, MLB
nonamecbs <- nonamecbs %>% mutate(playerid=str_c("cbs",Player,MLB),birth_year=NA,cbs_name=Player)
nonamecbs <- select(nonamecbs,playerid,Player,birth_year,cbs_name,Pos,MLB)
mymaster <- bind_rows(mymaster,nonamecbs)
```


remove any duplicates
```{r}

#mymaster <- unique(mymaster)

mymaster <- mymaster %>% distinct(playerid, .keep_all = TRUE)

```



Write out master file (playerid,Player,birth_year,cbs_name)
```{r}




# master <- read.csv("../master.csv",stringsAsFactors=FALSE, encoding="UTF-8")
# master <- dplyr::rename(master,playerid=fg_id,Pos = mlb_pos,MLB=mlb_team,Player=mlb_name)
# master <- mutate(master, birth_year = year(as.Date(birth_date, format="%m/%d/%Y")))
# master$playerid <- ifelse(str_length(master$playerid)==0,master$mlb_id,master$playerid)
# mymaster <- select(master,playerid,Player,birth_year,cbs_name,Pos,MLB)
write.csv(mymaster,"../mymaster.csv")
```


Summary statistics go here
```{r}
print(str_c("New ids from fangraphs = ",nrow(noidmatch)))
print(str_c("Combine rows (player+mlb) = ",nrow(sameName)))
print(str_c("Change MLB team (player only) = ",nrow(repl2)))
print(str_c("New players added from fangraphs = ",nrow(addthem)))
print(str_c("New players added from CBS = ",nrow(nonamecbs)))
```


Try adding year of birth from fangraphs
Fangraphs has put a block in place
```{r}

#mymaster <- mymaster %>% rowwise() %>% 
#  mutate(birth_year=ifelse(is.na(birth_year),getAge(playerid),birth_year))

noby <- filter(mymaster,is.na(birth_year),!str_starts(playerid,"cbs"),!str_starts(playerid,"my"))
nrow(noby)
#noby <- noby %>% slice_sample(n=100)
noby <- noby %>% rowwise() %>%
  mutate(birth_year=ifelse(is.na(birth_year),getAge(playerid),birth_year)) %>% select(playerid,nby=birth_year)

m2 <- left_join(mymaster,noby)
m2 <- mutate(m2,birth_year=ifelse(!is.na(birth_year),birth_year,nby))
mymaster <- select(m2,-nby)
write.csv(mymaster,"../mymaster.csv")
```


THIS IS THE END!

Can I find candidate duplicates?
Then I manually review and decide which ones to keep.
So far - they all seem to be FG ids - real one and 'sa' one
```{r}
m2 <- mymaster %>% select(Player,MLB)
dupes <- m2[duplicated(m2),]
print(dupes)

```




Here is some code to use CBS data to fill in with blank position master records.
NOTE: Fangraphs data does not include position data
```{r}

cbs2 <- rename(cbs,cbsPos = Pos)
my <- mutate(mymaster,Player=cbs_name)

forPos <- left_join(cbs2,my,by=c('Player','MLB'))
forPos <- select(forPos,playerid,cbsPos)

m2 <- left_join(mymaster,forPos)
m2 <- mutate(m2,Pos=ifelse(!is.na(cbsPos),cbsPos,Pos))
mymaster <- select(m2,-cbsPos)


```


After this is all about birth year and is either broken or limited


Can we get Baseball Reference to work for us?
We can download by year, different tables for hitting and pitching
https://www.baseball-reference.com/leagues/MLB/1991-births.shtml

NOTE:  This worked a little bit, but only for hitters, and one birthyear at a time
```{r}
byear <- '1990'
page <- read_html(str_c("https://www.baseball-reference.com/leagues/MLB/",byear,"-births.shtml")) %>% 
  html_nodes("table") 
df <- page[[1]] %>% html_table(,header=TRUE,fill=TRUE)
pl <- select(df,Player=Name,MLB=Tms) %>% separate_rows(MLB) %>% mutate(BRbirth_year=byear)

m2 <- left_join(mymaster,pl,by=c('Player','MLB'))
m2 <- mutate(m2,birth_year=ifelse(!is.na(birth_year),birth_year,BRbirth_year))
mymaster <- select(m2,-BRbirth_year)

noby <- filter(mymaster,is.na(birth_year))
nrow(noby)

```

More birth year stuff - never got this working
Lets see if we can get anything from Lahman database
```{r}
# people <- People %>% select(playerID,birthYear,nameGiven)
# pitching <- Pitching %>% select(playerID,yearID,teamID) %>% filter(yearID >= 2018)
# batting <- Batting %>% select(playerID,yearID,teamID) %>% filter(yearID >= 2018)
# team <- Teams %>% select(teamID,teamIDBR) %>% unique()
# 
# yp <- bind_rows(pitching,batting)
# lpl <- left_join(yp,people) %>% left_join(team) %>% 
#   select(Player=nameGiven,MLB=teamIDBR,birthYear)
# 
# m2 <- inner_join(mymaster,lpl,by=c('Player'))
# m2 <- mutate(m2,birth_year=ifelse(!is.na(birth_year),birth_year,birthYear))
#mymaster <- select(m2,-nby)

```

THE BOARD!  I can get ~800 ages from there
That added about 300 - probably run once a year
```{r}
# board <- read.csv('../fangraphs-the-board-data.csv',stringsAsFactors=FALSE, encoding="UTF-8")
# board <- select(board,playerid=playerId,Age) %>% mutate(nby = 2021 - Age) %>% select(-Age)
# 
# noby <- filter(mymaster,is.na(birth_year))
# nrow(noby)
# 
# m2 <- left_join(mymaster,board)
# m2 <- mutate(m2,birth_year=ifelse(!is.na(birth_year),birth_year,nby))
# mymaster <- select(m2,-nby)
# 
# 
# noby <- filter(mymaster,is.na(birth_year))
# nrow(noby)

```

Fix roster file
```{r}
#official file
#rosters <- read.csv(str_c("../",year,"Rosters1.csv"), encoding="UTF-8")

#miss <- anti_join(rosters,master,by=c('playerid'))
#miss2 <- miss %>% mutate(birth_year=NA,cbs_name=Player) %>% 
#  select(playerid,Player,birth_year,cbs_name,Pos,MLB)

#mymaster <- bind_rows(mymaster,miss2)
```

Fix hittertrend file
```{r}
htrend <- read.csv("../code/hTrend.csv")
h2 <- distinct(htrend)
h2 <- mutate(h2,ndate=parse_date_time(date, orders = c('mdy', 'ymd')))
#write.csv(h2,"../code/hTrend.csv")

```

