---
title: "R Notebook"
output: html_notebook
---

Create new master file with the following fields:
- playerid
- Player
- birth_year
- cbs_name

```{r}

library(tidyr)
library(dplyr)
library(stringr)
library("lubridate")
library(rvest)

source('./daflFunctions.r')

year <- '2021'

getAge <- function(playerid) {
  print(playerid)
  page <- read_html(str_c("https://www.fangraphs.com/players/nolan-jones/",playerid,"/stats"))
  byear <- page %>% html_node(".player-info__bio-birthdate td") %>% html_text() %>% 
    str_extract("[0-9/]{8,}") %>% mdy() %>% year()
  byear
}

read.cbs2 <- function(fn) {
  df <- read.csv(fn,skip=1,stringsAsFactors=FALSE, encoding="UTF-8")
  df <- mutate(df, Pos = pullPos(Player))
  df <- mutate(df, MLB = pullMLB(Player))
  df$Player <- unlist(lapply(df$Player,stripName))
  # Team abbreviations are not the same - find all discrepancies WAS->WSH
  df$MLB <- replace(df$MLB,df$MLB=='WAS','WSH')
  df$MLB <- replace(df$MLB,df$MLB=='CHW','CWS')

  # Create Team column
  #df <- mutate(df,Avail=str_replace(Avail,'\\.\\.\\.',''))
  #df <- left_join(df,nicks,by=c('Avail'))
  df$Team <- df$Avail
  #df$Team <- str_replace(df$Team,'W','Free Agent')
  df$Team <- ifelse(str_detect(df$Team,'W '),'Free Agent',df$Team)
  df <- select(df,-Avail)
  #addPlayerid(df)
}

```
Start with previous mymaster (playerid,Player,birth_year,cbs_name)
```{r}
mymaster <- read.csv("../mymaster.csv",stringsAsFactors=FALSE) %>% select(-X)

#cleanup any blank cbs_name
mymaster <- mutate(mymaster,cbs_name = ifelse(cbs_name=='',Player,cbs_name))
```



Start with a fangraphs ATC prediction file
Usually about 1400 players
Get Player, Team, playerid from here
Have to convert Team to MLB
```{r}

fgh <- read.csv(str_c('../atcH',as.character(year),'.csv',sep=''),stringsAsFactors=FALSE, encoding="UTF-8")
colnames(fgh)[1] <- 'Player'
fgh <- select(fgh,playerid,Player,Team)
fgp <- read.csv(str_c('../atcP',as.character(year),'.csv',sep=''),stringsAsFactors=FALSE, encoding="UTF-8")
colnames(fgp)[1] <- 'Player'
fgp <- select(fgp,playerid,Player,Team)

fgraphs <- bind_rows(fgh,fgp)

mlbmap <- read.csv("../data/MLBmap.csv",stringsAsFactors = FALSE)
fgraphs <- left_join(fgraphs,mlbmap)



noidmatch <- anti_join(fgraphs,mymaster,by=c('playerid'))

```
For matches, update MLB for trades, signings
```{r}
small <- select(fgraphs,playerid,MLB)
mymaster <- inner_join(mymaster,small,by=c('playerid'))
mymaster <- mutate(mymaster,MLB=ifelse(is.na(MLB.y),MLB.x,MLB.y)) %>% select(-MLB.x,-MLB.y)

```



If name and team are identical, replace the id
```{r}
sameName <- inner_join(noidmatch,mymaster,by=c('Player','MLB'))
repl <- select(sameName,playerid = playerid.y,newid = playerid.x)
mymaster <- left_join(mymaster,repl)
mymaster <- mutate(mymaster,playerid = ifelse(is.na(newid),playerid,newid)) %>% select(-newid)
```

If name is identical but team is different - update id AND MLB
```{r}
noidmatch <- anti_join(fgraphs,mymaster,by=c('playerid'))
sameName <- inner_join(noidmatch,mymaster,by=c('Player'))

repl <- select(sameName,playerid = playerid.y,newid = playerid.x,MLB = MLB.y, newMLB = MLB.x)
mymaster <- left_join(mymaster,repl)
mymaster <- mutate(mymaster,playerid = ifelse(is.na(newid),playerid,newid)) %>% select(-newid)
mymaster <- mutate(mymaster,MLB = ifelse(is.na(newMLB),MLB,newMLB)) %>% select(-newMLB)
```
Add new rows

```{r}
noidmatch <- anti_join(fgraphs,mymaster,by=c('playerid')) %>% mutate(birth_year=NA,cbs_name=Player,Pos='')
addthem <- noidmatch %>% select(playerid,Player,birth_year,cbs_name,Pos,MLB)

mymaster <- bind_rows(mymaster,addthem)


```

Try adding year of birth from fangraphs
```{r}

mymaster <- mymaster %>% rowwise() %>% 
  mutate(birth_year=ifelse(is.na(birth_year),getAge(playerid),birth_year))

```



What can I get from CBS?
There are a lot more rows in CBS than in fangraphs
```{r}
cbsH <- read.cbs2('../AllHitters.csv')
cbsH <- select(cbsH,Player,Pos,MLB)
cbsP <- read.cbs2('../AllPitchers.csv')
cbsP <- select(cbsP,Player,Pos,MLB)
cbs <- bind_rows(cbsH,cbsP)

my <- mutate(mymaster,Player=cbs_name)

nonamecbs <- anti_join(cbs,my,by=c('Player'))
```


```{r}

```



Write out master file (playerid,Player,birth_year,cbs_name)
```{r}




# master <- read.csv("../master.csv",stringsAsFactors=FALSE, encoding="UTF-8")
# master <- dplyr::rename(master,playerid=fg_id,Pos = mlb_pos,MLB=mlb_team,Player=mlb_name)
# master <- mutate(master, birth_year = year(as.Date(birth_date, format="%m/%d/%Y")))
# master$playerid <- ifelse(str_length(master$playerid)==0,master$mlb_id,master$playerid)
# mymaster <- select(master,playerid,Player,birth_year,cbs_name,Pos,MLB)
write.csv(mymaster,"../mymaster.csv")
```

